### 2013-06-13 replies.tex
just two minor corrections
Ref 3, replies 1 and 2

@@

@@

>>>>

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{As stated
in the abstract, our method allows to ``infer the matrix of potential
interactions among a pool of species'', and does so regardless of whether one is
working at the local or regional scale. In the text, we give examples at both
these scales (locally in figures 2 and 3, regionnaly in figure 5). We do agree
with the fact that additional information will make the predictions better; this
is described at length in the text, and an example of this (including
co-occurence along the depth gradient) is pictured in Fig. 5b. This is also
explicitely written in the discussion (L. XXX-XXX).}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We agree
that the fit of the model is only as strong as the relationship between prey and
predator body-size. This is the purpose of Fig. 3; this relationship is also
described in section 3.1 ``Predictive performance''.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected accordingly}}
